Open-Set Domain Adaptation through Self-Supervision

### 2022-02-10 paper/main.tex
Abstract rephrase

%%%%%%%%% ABSTRACT
\begin{abstract}
  Performance loss over the change of domain in deep learning applications is a common problem.
  Solving the issues usually relies on adapting the model to the new domain having at disposal large and labeled datasets, which is not always the case or cost-effective.
  In this paper we propose a new approach to the problem, to adapt in a robust manner a model to the new domain while not needing large amounts of data thanks to a self-supervised task.
  Experiments conducted on the Office-Home dataset show really promising results.
\end{abstract}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
  Performance loss over domain change is a common problem in machine learning applications.
  Solving the issue usually relies on adapting the model to the new domain by having at disposal large and labeled datasets, either rare or costly to acquire.
  In this paper we propose a new approach, adapting models to the new domains while not needing relying on labeled data thanks to a self-supervision.
  Experiments conducted on the Office-Home dataset show interesting results and method effectiveness.
\end{abstract}
